---
title: "Readme"
output: 
  github_document:
    html_preview: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r builddate, echo=FALSE}
paste0("Time of last build: ", Sys.time())
```


## Introduction

`R` files associated with data analysis and writing for this project.
This project uses the `drake` package to manage workflow and promote reproducibility.


### Requirements

- **NHD Plus**: This project utilizes the NHD National Seamless geodatabase. This is not included in the repository due to size. If you have a local copy, the source code can be modified to point to it. Otherwise, use `nhdplusTools` to download a copy.

```{r eval=FALSE}
nhdplusTools::download_nhdplusV2(outdir = here::here("data"))
```

- **Water Quality Data**: Water quality data was obtained from the Water Quality Portal (https://www.waterqualitydata.us/portal/) and is stored as a `.tsv` file under the `data/STORET` directory. The source data can be downloaded directly using the following URL: https://www.waterqualitydata.us/portal/#organization=TCEQMAIN&characteristicName=Escherichia%20coli&mimeType=tsv



### Set local paths

The `make.R` file should be updated with the appropriate file paths to `gdal v2.3.3` directory, the NHD geodatabase location, and NLCD data location. 

```{r eval=FALSE}
###########################
#### set local options ####
###########################
# gdal v2.3.3 or greater must be installed
# specify the path that gdal_warp.exe can be found
gdal_directory <- "C:\\Users\\User.Name\\AppData\\Local\\Continuum\\anaconda3\\Library"
# specify path to your nhdplus database
nhd_data <- here::here("data/NHDPlusV21_NationalData_Seamless_Geodatabase_Lower48_07/NHDPlusNationalData/NHDPlusV21_National_Seamless_Flattened_Lower48.gdb")
```


## Building the project

### Check for evidence of reproducibility

```{r eval=FALSE}
make(plan)
config <- drake_config(plan)
outdated(config)
```

### Replicate the project

```{r eval=FALSE}
clean() # removes author's results
source("R/packages.R")  # loads packages
source("R/dataRetrieval_functions.R")
source("R/exploratory_report_functions.R")
source("R/plan.R")      # creates the drake plan
make(plan)
```

## Info

### System config

```{r}
sessionInfo()
```