---
title: "Readme"
output: 
  github_document:
    html_preview: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


[![License: CC BY 4.0](https://img.shields.io/badge/License-CC%20BY%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)


```{r builddate, echo=FALSE}
paste0("Time of last build: ", Sys.time())
```


## Introduction

This project uses the `drake` package to manage workflow and promote reproducibility.

Research data and metadata are located in:

```
data/cleaned_data.csv
data/flow_adjusted_mk_results.csv
data/unadjusted_mk_results.csv
data/metadata/
```

## Reproduce the Project

If you would like to reproduce the project please follow the suggested guidelines below. The required R packages are detailed at the end.

### Requirements

- **NHD Plus**: This project utilizes the NHD National Seamless geodatabase. This is not included in the repository due to size. If you have a local copy, the source code can be modified to point to it. Otherwise, use `nhdplusTools` to download a copy.

```{r eval=FALSE}
nhdplusTools::download_nhdplusV2(outdir = here::here("data"))
```


## Building the project

### Check for evidence of reproducibility

```{r eval=FALSE}
library(drake)
make(plan)
config <- drake_config(plan)
outdated(config)
```

### Replicate the project

```{r eval=FALSE}
clean()
source("R/packages.R")  
source("R/download_data.R")
source("R/mann-kendall-tests.R")
source("R/logistic_regression.R")
source("R/figures.R")
source("R/tables.R")
source("R/plan.R")  

###########################
#### set local options ####
###########################

# specify path to your nhdplus database
nhd_data <- "E:\\TWRI\\Data-Resources\\NHDPlusV21_NationalData_Seamless_Geodatabase_Lower48_07\\NHDPlusNationalData\\NHDPlusV21_National_Seamless_Flattened_Lower48.gdb"

##########################################################
#### You shouldn't need to modify anything after this ####
##########################################################

nhdplus_path(nhd_data)

make(
  plan
)
```

## Info

### System config

```{r}
sessionInfo()
```